### 2020-06-20 docs/LaTex/Paper.tex
Minor fixes
Minor changes

\subsubsubsection{Arduino sketch}
The sketch to take advantage of LoRa Shield is mainly based on the LoRaMAC-in-C library (\cmd{lmic})\footnote{Dragino has a \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered as less accurate than the MCCI version, which is a fork itself from the first port of LMIC library by Matthijs Kooijman.} implemented by \href{https://mcci.com/}{MCCI} whose technical documentation can be found in \cite{MCCI_lmic}

\doubt{}

>>>>

\subsubsubsection{Arduino sketch}
In order to this sketch takes advantage of the plugged LoRa Shield, is required to base it on the LoRaMAC-in-C library \cite{MCCI_lmic} (\cmd{arduino-lmic})\footnote{Dragino has a \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered as less accurate than the MCCI version, which is a fork itself from the first port of LMIC library by \href{https://github.com/matthijskooijman}{Matthijs Kooijman}.} implemented by \href{https://mcci.com/}{MCCI}, whose technical documentation can be found in \cite{MCCI_lmic_docs}
